---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# imfweo

<!-- badges: start -->
<!-- badges: end -->

`imfweo` provides easy access to the International Monetary Fund's World Economic Outlook (WEO) database in R. This is a minimum viable product under heavy development.

## Features

* Download and process WEO data releases
* List available countries, indicators, and releases
* Extract specific series for analysis
* Consistent interface and tidy data output

## Installation

You can install the development version of imfweo from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Teal-Insights/imfweo")
```

## Basic Usage

### Getting WEO Data

You can get WEO data either by downloading specific series for selected countries (`weo_get()`) or by downloading complete WEO releases (`weo_bulk()`).

Get specific indicators for selected countries:
```{r specific_data}
library(imfweo)

# Get GDP growth and inflation for G7 countries
weo_get(
  series = c("NGDP_RPCH", "PCPIPCH"),  # Real GDP growth and inflation
  countries = c("USA", "GBR", "DEU", "FRA", "ITA", "JPN", "CAN"),
  start_year = 2015
)
```

Download a complete WEO release:
```{r bulk_data}
# Download Spring 2024 WEO
weo_bulk(2024, "Spring")
```

### Available Data

List available WEO releases:
```{r releases}
weo_list_releases()
```

List available countries and regions:
```{r countries}
weo_list_countries()
```
```{r countries specific}
# Search for specific countries
weo_list_countries("united")
```


List available economic indicators:
```{r series}
weo_list_series()
```

```{r series specific}
# Search for GDP-related indicators
weo_list_series("gdp")
```


## Development Status

This package is under active development. Current features are working but may change. Future releases will add:

* Better data validation
* More convenience functions for common analyses
* Improved documentation and vignettes
* Additional data transformation tools

## Contributing

Contributions are welcome! Please submit issues and pull requests on GitHub.

## License

MIT + file LICENSE
