---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# imfweo

<!-- badges: start -->
<!-- badges: end -->

`imfweo` provides easy access to the International Monetary Fund's World Economic Outlook (WEO) database in R. This is a minimum viable product under heavy development.

## Features

* Download and process WEO data releases
* List available countries, indicators, and releases
* Extract specific series for analysis
* Consistent interface and tidy data output

## Installation

You can install the development version of imfweo from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("teal-insights/r-imfweo")
```

## Usage

The main function `weo_get()` provides a simple interface to download data from the latest World Economic Outlook (WEO) publication:

```{r}
library(imfweo)

weo_get()
```

On the first run of each R session, the function may take a few seconds to execute as the package checks which WEO publication is currently the latest. This information is put into a cache that is reset whenver your session restarts. 

To explicitly retrieve the most recent publication metadata, use:

```{r}
weo_get_latest_publication()
```

To fetch data from a specific publication, or to filter by country, indicator, or time range, you can use the available parameters:

```{r}
weo_get(
  series = c("NGDP_RPCH", "PCPIPCH"),  # Real GDP growth and inflation
  countries = c("USA", "GBR", "DEU", "FRA", "ITA", "JPN", "CAN"),
  start_year = 2015
)
```

Download a complete WEO release:
```{r bulk_data}
# Download Spring 2024 WEO
weo_bulk(2024, "Spring")
```

### Available Data

List available WEO releases:
```{r releases}
weo_list_releases()
```

List available countries and regions:
```{r countries}
weo_list_countries()
```
```{r countries specific}
# Search for specific countries
weo_list_countries("united")
```


List available economic indicators:
```{r series}
weo_list_series()
```

```{r series specific}
# Search for GDP-related indicators
weo_list_series("gdp")
```


## Development Status

This package is under active development. Current features are working but may change. Future releases will add:

* Better data validation
* More convenience functions for common analyses
* Improved documentation and vignettes
* Additional data transformation tools

## Part of the econdataverse

`imfweo` is part of the [econdataverse](https://www.econdataverse.org/), a universe of open-source packages designed to make working with economic data seamless and efficient. The goal is simple: spend less time wrestling with data and more time analyzing it.

Think of econdataverse packages as LEGO® pieces - modular tools designed to work together perfectly. For example, you might combine World Bank debt data (using [{wbids}](https://teal-insights.github.io/r-wbids/)) with IMF macroeconomic projections from this package.

### Current Features

- Download WEO data programmatically
- Access specific indicators for selected countries
- Get metadata about available series and countries
- Return data in tidy format ready for analysis

### Roadmap

We're working on:

- Standardizing country names across econdataverse packages
- Creating consistent column names and data structures
- Building tools for common economic analyses
- Making data combination across sources seamless

Other econdataverse packages:

- [{wbids}](https://teal-insights.github.io/r-wbids/): World Bank International Debt Statistics ✅
- [{wbwdi}](https://tidy-intelligence.github.io/r-wbwdi/): World Bank World Development Indicators 🚀
- More coming soon!

Our mission is to unclog the data bottleneck in economic analysis. By making data access and cleaning efficient and consistent, we enable policymakers and researchers to focus on what matters: using data to make better decisions in a world of limited resources.
